---
title: "Data management"
subtitle: "CDS 2022 BTS workshop"
author: "Rick Gilmore & Kasey Soska"
date: "`r Sys.time()`"
output:
  ioslides_presentation:
    css: css/ioslides.css
    logo: img/PLAY-leaf.png 
    widescreen: true
    incremental: false
    transition: default
---

## Acknowledgements

- Support from NICHD, NIH OD, NIMH, NIDA, OBSSR, NSF
- Karen Adolph, Cathie Tamis-LeMonda, Orit Hertzberg, Tiger Teng

## Overview

- A cautionary tale
- (Hyper)active Curation

# A cautionary tale

---

<!-- Data Sharing and Management Snafu in 3 Short Acts -->

<iframe width="560" height="315" src="https://www.youtube.com/embed/66oNv_DJuPc" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

<small>[[@NYU_Health_Sciences_Library2013-gp]](https://www.youtube.com/watch?v=66oNv_DJuPc)</small>

# (Hyper)active curation

## What is it?

- Embed data curation within data collection workflow
- Conduct rigorous quality assurance (QA) during collection
- Curate data with specific sharing target in mind

## Workflow

## Quality assurance (video)

- Show semi-automated QA reports from Databrary

## Data export & cleaning (surveys)

```{r, child="splash.Rmd"}
```

```{r, child="resources.Rmd"}
```