---
title: "Play & Learning Across a Year (PLAY)"
author: "Rick Gilmore & Kasey Soska"
subtitle: "CDS 2022 BTS workshop"
date: "`r Sys.time()`"
output:
  ioslides_presentation:
    css: css/ioslides.css
    logo: img/PLAY-leaf.png 
    widescreen: true
    incremental: false
    transition: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, 
                      message = FALSE,
                      fig.align = "center",
                      out.width = "800px")
```

## Acknowledgements

- Support from NICHD, NIH OD, NIMH, NIDA, OBSSR, NSF
- Karen Adolph, Cathie Tamis-LeMonda, Orit Hertzberg, Tiger Teng

## Overview

- What is PLAY
- Why PLAY
- Challenges to face
- Challenges met
- Challenges yet-to-be-met

# What is PLAY

<!-- Insert PLAY video from Databrary Board -->

---

- 1,000 mother-infant dyads (12-, 18-, 24-mos)
- 1 hr natural behavior (video)
- 5 min structured play (video)
- House tour (video)
- Parent-report questionnaires

---

- Foundational video coding passes
    - Speech \& language
    - Emotional expression
    - Object interaction
    - Locomotion \& physical activity
    
---

- Common, shared data
- Rigorous QA control
- But investigator-specific questions...
- Dataset as deliverable
- Catalyze/expand capacity to exploit video

# Why PLAY

## Natural behavior

## Big data developmental science

## Open science

- Full transparency
- Re-useability

# Challenges to face

## Sampling

- Age range(s)
- What language backgrounds...
- Where to sample...
- What to vary, what to keep constant...
- Is 'an hour in the life' representative?

# Challenges met

- Only English and Spanish
- Informed by Census demographics

# Challenges yet-to-be-met

- Findable, useable beyond launch group
- Limitations of Databrary 1.0
    - Virtual volumes?
- Versioning data, protocol, coding scheme
- Add-on, follow-up studies
    - New data
    - Augmented, new annotations

```{r, child="splash.Rmd"}
```

```{r, child="resources.Rmd"}
```